Title here

### 2017-01-03 portfolio/text/ms.Rmd
More abstract editing

Individuals who rely on the extraction of natural resources for their
livelihood --- fishers, farmers, and loggers, among others --- face high levels
of income variability driven by a mix of environmental, biological, and
economic variability.
A key component to managing these industries is identifying how regulatory
actions and individual behaviour affect income variability and by extension the
economic stability and sustainable use of natural resources. For commercial
fisheries, recent work has identified that communities and vessels can lower
revenue variability by increasing the diversity of species fished. 
<!-- fix: One sentence clearly stating the general problem being addressed by
this particular study --> 
However, it is unclear if ... extend to individual... year to year changes
<!-- cut down, 1 sentence: -->
Here we identify three axes by which fishers in Alaska, one of the world's most
productive fishery regions, can potentially diversify fishing activities and
investigate how individual actions along each diversity axis affect revenue and
revenue variability. 
<!-- We simultaneously assess the value to individual fishers of choosing to (1) own -->
<!-- permits that allow targeting a diverse fish species assemblage, (2) diversify -->
<!-- by adding additional permits, or (3) catch a greater species diversity within -->
<!-- the constraints of a given permit. --> 
We show that fishing permits with higher species diversity reduces revenue
variability and fishing an additional permit is associated with higher revenue
and lower variability. However, increasing species diversity within the
constraints of a permit set has a fishery-dependent effect on revenue and is
usually (`r g2_dens`% probability) associated with increased uncertainty in
revenue the following year. 
Our results suggest that the benefit of species diversity for reducing revenue
variability is mostly an across-permit effect, not a benefit that can be easily
harnessed by individual permit holders. The most effective mechanism for
increasing revenue and decreasing variability --- purchasing permits to
participate in additional fisheries --- is also the most costly and often
limited by regulations such as limited entry and catch share programs.

>>>>

Individuals who rely on the extraction of natural resources for their
livelihood --- fishers, farmers, miners, and loggers, among others --- face
high levels of income variability driven by a mix of environmental, biological,
and economic variability.
A key component to managing these industries is identifying how regulatory
actions and individual behaviour affect income variability and by extension the
economic stability and sustainable use of natural resources. For commercial
fisheries, recent work has identified that communities and vessels can lower
revenue variability by increasing the diversity of species fished. 
<!-- fix: One sentence clearly stating the general problem being addressed by
this particular study --> 
However, it is unclear if ... extend to individual... year to year changes
<!-- cut down, 1 sentence: -->
Here we identify three axes by which fishers in Alaska, one of the world's most
productive fishing regions, can potentially diversify fishing activities and
investigate how individual actions along each axis affect revenue and revenue
variability. 
<!-- We simultaneously assess the value to individual fishers of choosing to (1) own -->
<!-- permits that allow targeting a diverse fish species assemblage, (2) diversify -->
<!-- by adding additional permits, or (3) catch a greater species diversity within -->
<!-- the constraints of a given permit. --> 
We show that fishing permits with higher species diversity reduces revenue
variability and fishing an additional permit is associated with higher revenue
and lower variability. However, increasing species diversity within the
constraints of a permit set has a fishery-dependent effect on revenue and is
usually (`r g2_dens`% probability) associated with increased revenue uncertainty
the following year. 
Our results demonstrate that the most effective option for individuals to
increase revenue and decrease variability is to purchase permits to participate
in additional or more diverse fisheries. However, this option is costly
and often limited by regulations such as limited entry and catch share
programs.
With increasing environmental variability in a changing climate, it will be
particularly important that individuals who rely on natural resources for
their livelihood have effective strategies to reduce income variability.
